Tigth Bounds for Online Balanced Graph Partitioning

### 2020-05-08 paper/disc20clustering.tex
More restructuring

\section{PPL Algorithm} \label{alg:PPL}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\begin{algorithmic}
		%        \Require 
		%        $k, \ell$,
		%        initial configuration $P_I$,
		%        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
		%        \Ensure A final configuration $P_F$ 
		\STATE {For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$}
		\STATE{$P_0 := P_I$}
		\label{line:initcomponents}
		\FOR {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
		\STATE Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
		\IF{$C_1 \neq C_2$}
		\STATE {Unite the two components into a single component $C'$ and
		$\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$} \label{line:mergecomponents}
		\IF{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$
		\COMMENT{i.e.~if not in the same cluster}    
		}       
		\STATE {$P_{t} = \mathit{repartition}(P_{t-1}, P_I, \mathcal{C})$} 
		\COMMENT{move to $P$ closest to $P_I$}
		\label{line:rebalance} 
		\ENDIF
		\ENDIF
		\ENDFOR
	\end{algorithmic}
	\caption{Perfect Partition Learner (\PPL)}
	\label{alg:ppl}
\end{algorithm}

@@

\section{The Partitioning Problem}
\label{sec:part}

@@

\subsection{Improved analysis of the component-based algorithm}
\label{sec:k3}

@@

\subsection{Warm-up: bounding the reconfiguration for $k=3$}

Corollary: DET2 is $O(\ell)$-competitive for $k=3$.

\section{Improved algorithm for Online Rematching}
\label{sec:k2}

>>>>

\label{alg:PPL}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\begin{algorithmic}
		%        \Require 
		%        $k, \ell$,
		%        initial configuration $P_I$,
		%        sequence of  requests $\sigma_1, \dots, \sigma_N$ 
		%        \Ensure A final configuration $P_F$ 
		\STATE {For each node $v$ create a singleton component $C_v$ and add it to $\mathcal{C}$}
		\STATE{$P_0 := P_I$}
		\label{line:initcomponents}
		\FOR {each  request $\sigma_t=\{u,v\}, 1 \leq t \leq N$}
		\STATE Let $C_1 \ni u$ and $C_2 \ni v$ be the container components
		\IF{$C_1 \neq C_2$}
		\STATE {Unite the two components into a single component $C'$ and
		$\mathcal{C} = (\mathcal{C}\setminus\set{C_1, C_2}) \cup ~\set{C'}$} \label{line:mergecomponents}
		\IF{$\mathit{cluster}(C_1, P_{t-1}) \neq \mathit{cluster}(C_2, P_{t-1})$
		\COMMENT{i.e.~if not in the same cluster}    
		}       
		\STATE {$P_{t} = \mathit{repartition}(P_{t-1}, P_I, \mathcal{C})$} 
		\COMMENT{move to $P$ closest to $P_I$}
		\label{line:rebalance} 
		\ENDIF
		\ENDIF
		\ENDFOR
	\end{algorithmic}
	\caption{Perfect Partition Learner (\PPL)}
	\label{alg:ppl}
\end{algorithm}

@@

\section{General Partitioning Model}
\label{sec:part}

Now  we discuss the general online
model where the request sequence
can be arbitrary.
In Section~\ref{sec:k3}, we show that the classic \emph{rent-or-buy} approach~\cite{karlin-ski-rental} provides an optimal algorithm for $k=3$.
Then, in Section~\ref{sec:k2}, we show a strictly $6$-competitive algorithm for $k=2$.

\subsection{An Optimal Algorithm for Clusters of Size $3$}
\label{sec:k3}

@@

@@

\subsection{Improved algorithm for Online Rematching}
\label{sec:k2}
